### 2020-01-23 experiments.tex
more python

>>>>

\begin{figure}
  \url{https://stackoverflow.com/questions/1428872/pylint-pychecker-or-pyflakes}
  \url{https://www.reddit.com/r/Python/comments/ii3gm/experience_with_pylint_pychecker_pyflakes/}
  \url{https://www.slant.co/versus/12630/12631/~pylint_vs_pyflakes}
  \url{https://news.ycombinator.com/item?id=12748885}
  \url{https://doughellmann.com/blog/2008/03/01/static-code-analizers-for-python/}
\caption{Blog posts and forum threads discussing Python static analysis tools.}
\label{fig:blogpython}
\end{figure}

For {\bf RQ3}, there were again no academic comparisons we could find.  However, opinions on the web were quite common (see Figure \ref{fig:blogpython} lists ones we examined.  It is hard to summarize the overall opinion here, since it ranges.  There is probably general agreement that PyChecker is old and maybe less useful, but also terse and sometimes helpful.  Pylint is the most recommended tool, and the general complaint that it is too picky was mitigated in our results by turning off clearly informative-only findings; users not configuring Pylint will probably see even more killed mutants, but likely a worse mutant ratio because mutants tend to introduce non-stylistic problems.  Pyflakes is well liked, and supposedly less verbose than Pylint; we did not see this, but that may be because pyflakes aims to focus on ``actual bugs'' so it is equally verbose for mutants, which are likely to be actual bugs.
